---
title: "IHME Data Landscaping 2022"
#author: "Christian Hernandez (chrish47@uw.edu), Helen Ippolito (helenipp@uw.edu)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}

```

# Using the Source Counts Function
(1) Make sure you are on the cluster for this, and that have you have an R interactive session opened. Please see the HUB for more details.  
(2) Script: "/ihme/scratch/projects/rgud/Source Counts Tool 2022/Code/Source Counts Code/source_counts_master.R"  
    • Run this on your console: `source("/ihme/scratch/projects/rgud/Source Counts Tool 2022/Code/Source Counts Code/source_counts_master.R")`  
    • Source counts function: `source_counts()`  
(3) Source in your location_data. REQUIRED.   
    • Function: `get_location_metadata()`  
    • Most common *location_set_id: 35*  
    • Please use the *location_data* object name.  
(4) When using the source_counts(), please make sure your out_path filepath exists.  
(5) For examples calls and explanations, please see the section below Title 'Example Calls'.    

# Source Counts Strategy - Mechanics

##### **We Can Only Count 'Sources' That Meet The Following Criteria**
• It is a GBD project with data that comes through our sources data ingestion pipeline. We don't count custom data outside our sources database.  
• The source data corresponds to valid NIDs that are published in the GHDx. Our source counts are all based on GHDx Record NIDs.  
• The source counts requested can be fulfilled with the data we have in our sources database / source counts tables. Data we have in-house. 


##### **General NID strategy Overview**
(1) ***NID Relationships***  
    • If a Record NID has an underlying NID, the underlying NID is used. [Ask Modelers If their pipeline have these?]  
    • If a record NID or replaced underlying NID is a Merged Citation, we break apart the Merged Citation into its associated Record NIDs.
(2) ***NID’s Data Type***  
    • Every GHDx Record NID has a data type (it is required).  
    • In some counting strategies, records are counted differently depending on data type. 
(3) ***NID Validity***  
    • NIDs must be valid, published, Record NIDs from the GHDx. We do not count “file” NIDs, “series or system” NIDs, aggregate NIDs, or any fake NIDs. 
    
##### **Source Counting Method**  
• Source counts will be generated using the following Counting Strategy Combination  

`NID + location + year_start + year_end`

• The above combination strategy is applied accross all data types, including: Scientific literature, Financial record, Survey, Census, and Clinical trial. As per the      GBD strategy, these type of sources should only be counted as per NID, instead of a combination. For the Maternal Data Landscaping Project(2022), these were counted using  the above combination as with other source types, in order to adequately cover the year and location spread better. 


[For more details on the GBD Source Counts strategy, please click here](https://hub.ihme.washington.edu/display/SCDS/Source+Counts+-+Source+Counting+Strategy)

# Source Counts Code


# Example Calls
